\rule{350pt}{5pt}\\ \textbf{An Extension of Optimal Teaching For Online Perceptrons} \\ \rule{350pt}{1pt}

### 2017-05-05 paper_final.tex
Added discussion section

\section{Conclusion}

>>>>

\section{Discussion}
Here we've shown some interesting bounds. Though not all tight they still highlight some of the security risks of perceptrons. If a perceptron were used on a web-server, any of these algorithms would be efficient enough to hack the perceptron to believe whatever decision boundary we like. As well these findings highlight the power of lying in Machine Teaching. With the ability to lie, teaching a perceptron becomes trivial. One further venture would be to look into other learning algorithms that could be taught efficiently with lying.
